\setchapterpreamble{\dictum[TCU Baseball]{So believe that voice that says that you can run a little faster and you can throw a little harder, that for you, the laws of physics are merely a suggestion.}}

\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

First and foremost, I want to thank Monika for making the present thesis possible and supporting me selflessly on my journey over the last few years.
Second, I want to thank Hans for welcoming me to the group and looking out for me.
Hans persistently challenged my physical understanding by never giving in to shortcuts in my explanations and sharing his unbiased and unorthodox perspectives as an engineer.
Third, I want to thank Fred for the many funny moments and shared laughter.
Fred's sharp mind quickly uncovered the logical fallacies in my many ideas, crucial for separating the good from the bad.
Regardless of what day or time, Fred was always open to my inquiries without judging their quality.
Fourth, I want to thank Stefano for the entertaining anecdotes from his rich life experience.
I will especially keep in mind the whiteboard sessions, where he inspired me with his combination of precision and creativity.
Fifth, I want to thank Momtchil for being available to the most unchristian times and keeping me clear of administrative burden.
Momtchil's passion for advanced mathematical concepts and humorous stories about eastern Europe will remain in my memory.

I hope this work conserves a tiny fraction of the enormous knowledge aggregated by Hans, Fred, Stefano, and Momtchil and correctly reflects their unique contributions to \gls{qkd}.
In particular, I tried to adhere to Fred's quantum information expertise in \Cref{ch:qkd} and Stefano's insights on macroscopic electrodynamics and the modulators in \Cref{ch:components}.
Hans's profound knowledge in signal processing guided me in drafting \Cref{ch:system}.
His criticisms of the quadrature measurement, one of many initial motivations for this work, led to the generalized quadrature operator in \Cref{ch:components}.
For the final proof-readings, I want to thank Dominik, Hans, Marianne, Markus.

Although not directly contributing to this thesis, I want to thank my family and friends for being here with me.
Especially, I want to thank my grandmother and mother for taking care of me whenever I needed to recharge from work.
Furthermore, I owe a deep debt to Julia, who helped me gain confidence in myself and motivated me to pursue this thesis.
Finally, I want sincerely welcome my dear friends, including Abdullah, Anxiang, Chris, Daniel, Daniele, Dominik, Fabian, Haci, Jonas, Markus, Marvin, Max, Michael, Nils, Roman and Myriam, Stefan, Valentin, and Wolfang, for accepting me for who I am and the shared memories.
